Regular singular Volterra equations on complex domains

### 2023-08-25 reg-sing-volterra.tex
Clean up revisions related to cond:sing

In addition, for each $\sigma > \tau$, the bound
\[ |\hardker(a, a')| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
%%by bringing $a$ and $a'$ close enough to $\zeta = 0$.
%%is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
We'll assume that $\tau$ is real and positive.

@@

\section{A motivating example}\label{sec:example}
%\color{black}
%\section{\textcolor{orange}{[Proof of main results]}}
We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain. The latter is an example of the regular singular Volterra equations we introduced above.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
%%\begin{equation}\label{eqn:level 1 ode}
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
%%\end{equation}
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
converge in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}. In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}. 
\subsection{\textcolor{orange}{Notation}}
\item Previously, we always looked at Volterra operators with a regular singularity at $\zeta = 0$.
\item When we try to solve a level~1 differential equation, we'll get an operator with many regular singularities---one at each root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
\item Rules for working at $\zeta = \alpha$:
    \item In all our work from Sections~\ref{sec:intro}--\ref{sec:proof_main_results}, the role of the coordinate $\zeta$ is played instead by $\zeta - \alpha$. Concrete examples of how to do that:
        \item References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.
        \item Conditions on operators, location of regular singularity.
        \item Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.
        \item Definition of $\singexp{\sigma}{\Lambda}$ spaces.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

@@

\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain} replacing the origin $\zeta=0$ with $\zeta=\alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

@@

\begin{thm}\label{thm:example}
For each root $-\alpha$ of $P$, the equation
\[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
has a unique solution $\psi_\alpha$ in the affine subspace
\[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
%%The equation $\hat{P}_\alpha\psi_\alpha=0$ has a unique solution of the form
%%\[ \psi_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
%%\[\psi_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
%%where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}
%%\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

\begin{proof}
Choose a root $-\alpha$ of $P$. For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.

@@

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
It follows that

\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
\end{align*}

Now we expand $Q$ at $\zeta=\alpha$ writing $Q=Q(-\alpha)+(\zeta-\alpha)Q_\text{extra}(\zeta)$ and we continue the previous computations, getting

\begin{align}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & \notag =
 \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
 &\label{eqn:step} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} 
 \end{align}

First we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded when $a$ is close enough to $\zeta = \alpha$. In fact we have

\begin{align*}
-\frac{Q(-\zeta(a))}{P(-\zeta(a))} & =
\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a) - \alpha)\,Q_\text{extra}(\zeta(a))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
 \end{align*}

Define $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$, then

\[-\frac{Q(-\zeta(a))}{P(-\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)}\]

Since $Q$ is a polynomial, by bringing $a$ close enough to $\zeta=\alpha$ we can bound both $Q(-\zeta(a))/(\zeta(a)-\beta)$ and $Q_\text{extra}(\zeta(a))$.

Then, we want to prove that for all $\sigma > \tau_\alpha$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$. From Equation \eqref{eqn:step}, taking the absolute value we get

\begin{align*}
\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| \\
|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|
\end{align*}

Notice that by bringing $\zeta(a')$ close enough to $0$ we can make the middle term

\[\left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right|\]

arbitrary small. Similarly, by bringing also $\zeta(a)$ close to $0$ we can make the first term

\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right|\]

as small as we want. Hence, setting $\tau_\alpha=\left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|$, we have that for any $\sigma>\tau_\alpha$

\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma. \]

 %Want: for all $\sigma > \tau$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.

\color{RoyalBlue}
\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}
\end{align*}
As $a$ and $a'$ approach $\zeta = \alpha$, the
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
part approaches the limit
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Now we just have to deal with the term
\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)}. \]
%%From the fact that
%%\[ Q(-\zeta) \in Q(-\alpha) + O\big(|\zeta - \alpha|\big) \]
%%at $\zeta = \alpha$, we reason that
%%\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)} \in \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a)-\alpha)} + O(1) \]
%%at $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$.

\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\]
is bounded as $\zeta(a')$ approaches $\alpha$.
\color{DarkTurquoise}
\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)(\zeta(a)-\alpha)}\right|< C  \]

we know
\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\right|< C  \]

Conversely, as $a'$ approaches $\zeta=\alpha$, the term

\[\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}\]

converges to $\frac{\tau_\alpha}{\zeta(a)-\alpha}$ with $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$. We conclude that 
\[-\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}\]

>>>>

In addition, for each $\sigma > \tau$, the bound
\[ |\hardker(a, a')| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
We'll assume that $\tau$ is real and positive.

@@

\section{A motivating example}\label{sec:example}
%\color{black}
%\section{\textcolor{orange}{[Proof of main results]}}
\subsection{Overview}
We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain. The latter is an example of the regular singular Volterra equations we introduced above.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
%%\begin{equation}\label{eqn:level 1 ode}
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
%%\end{equation}
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
converge in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}. In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}. 
\subsection{\textcolor{orange}{Notation}}
Previously, we studied Volterra operators with a regular singularity at $\zeta=0$. However, when we study solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$. Therefore, we have to set the notation, to deal with this more general situation.

Here, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to be able to deal with singularities different from the origin. In fact, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.

\begin{brainstorm}
\item Previously, we always looked at Volterra operators with a regular singularity at $\zeta = 0$.
\item When we try to solve a level~1 differential equation, we'll get an operator with many regular singularities---one at each root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
\item Rules for working at $\zeta = \alpha$:
\begin{itemize}
    \item In all our work from Sections~\ref{sec:intro}--\ref{sec:proof_main_results}, the role of the coordinate $\zeta$ is played instead by $\zeta - \alpha$. Concrete examples of how to do that:
    \begin{itemize}
        \item References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.
        \item Conditions on operators, location of regular singularity.
        \item Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.
        \item Definition of $\singexp{\sigma}{\Lambda}$ spaces.
    \end{itemize}
\end{itemize}
\end{brainstorm}
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

@@

\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain}, replacing the origin $\zeta=0$ with $\zeta=\alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

@@

\begin{thm}\label{thm:example}
For each root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive, the equation
\[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
has a unique solution $\psi_\alpha$ in the affine subspace
\[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
\end{thm}
\begin{proof}
Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.

@@

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
It follows that
\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
\end{align*}
Now we expand $Q$ around $-\alpha$, using the decomposition $Q(\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(\zeta)$ to split up the last term of the expression above:
\begin{align}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} %% & \notag = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
&\label{eqn:split-numerator} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} 
\end{align}
First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. Equation~\eqref{eqn:split-numerator} tells us that
\begin{align*}
-\frac{Q(-\zeta)}{P(-\zeta)} & =
\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
\end{align*}
Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)}\]
Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.

Next, we want to show that for any $\sigma > \tau_\alpha$, the bound
\[ |\zeta(a) - \alpha| \left|\frac{q(a')}{p(a)}\right| < \sigma \]
holds when $a$ and $a'$ are close enough to $\zeta = \alpha$. Taking the absolute value of both sides of Equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
\begin{align*}
\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right| + \tau_\alpha.
\end{align*}
By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
\[\left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right|\]
as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right|\]

as small as we want. Hence, for any $\sigma > \tau_\alpha$, the bound
\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$.
\begin{verify}
\par Solution of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}
